Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2023-02-08 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

We have theoretical specrtra of CN shown in Figure~\ref{fig:CN_theory}.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
        \caption{Theoretical cross section spectra of CN for 100K and 1000K.}
        \label{fig:CN_theory}
        \script{plot_two_CN_temps.py}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/ccf.pdf}
        \caption{Cross correlation for different number densities of CN.}
        \label{fig:ccf}
        \script{plot_ccf.py}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
        \caption{Cross correlation for different number densities of CN averaged over many spectra.}
        \label{fig:ccf}
        \script{plot_ccf_mean.py}
    \end{centering}
\end{figure}
